### 2022-01-10 acks.tex
version 11 jan

\section*{Acknowledgements}\label{sec:acks}
\todo[inline]{TODO: James? Funding? Project course students?}

>>>>

\section*{Acknowledgements}\label{sec:acks}

This research has been partially funded by
\begin{enumerate*}[itemjoin={{; }}, itemjoin*={{; and }}]
    \item the VINNOVA Competence Center for \ac{TECoSA} at KTH Royal Institute of Technology
    \item the \ac{SSF}, through grant number ITM17--0246, awarded to James Gross, Ph.D.
\end{enumerate*}
Any opinions, findings, conclusions or recommendations expressed in this material are those of the authors and do not necessarily reflect the view(s) of their employers or funding sources.

We also wish to thank S. Mostafavi, V. N. Moothedath, N. Roy, M. Alsakati, O. Ferm, and S. Vojcic, without whose effort and support this work not have been possible.

### 2022-01-10 intro.tex
version 11 jan

A subcategory of \acp{CPS} which stands to particularly benefit from the adoption of the above technologies is \acp{NCS}~\cite{Gupta2010NCSOverview}, a type of \ac{CPS} wherein multiple networked actuators and sensors form a part of the same automatic control system.
Depending on the physical system being controlled, \acp{NCS} can have stringent timing and reliability requirements for the communication between components that conventional cloud paradigms and cellular networks are unable to meet~\cite{Liu2017Review,Wan2020Efficient}.

>>>>

A subcategory of \acp{CPS} which stands to particularly benefit from the adoption of the above technologies is \acp{NCS}~\cite{Gupta2010NCSOverview}, a type of \ac{CPS} wherein multiple networked actuators and sensors form a part of the same automatic control system.
Depending on the physical system being controlled, \acp{NCS} can have stringent timing and reliability requirements for the communication between components that conventional cloud paradigms and cellular networks are unable to meet~\cite{Wan2020Efficient}.
